### 2009-08-28 docs/runtime_parameters/runtime_parameters.tex
in the middle of consolidating all of the sponge.f90 into one file (except for XRB)
make ppm_type=1 the default for all problems except xrb

\verb=  ppm_type  = &   0 = no ppm \newline 1 = 1985 ppm \newline 2 = 2009 ppm  &  0 \\

@@

\verb=  s0_interp_type  = &   The interpolation for filling a cell-centered multifab from a 1D bin-centered array. \newline 1 = piecewise constant; \newline 2 = piecewise linear; \newline 3 = quadratic  &  1 \\

@@

@@

>>>>

\verb=  ppm_type  = &   0 = no ppm \newline 1 = 1985 ppm \newline 2 = 2009 ppm  &  1 \\

@@

\verb=  s0_interp_type  = &   The interpolation for filling a cell-centered multifab from a 1D bin-centered array. \newline 1 = piecewise constant; \newline 2 = piecewise linear; \newline 3 = quadratic  &  3 \\

@@

\verb=  sponge_center_density  = &   Center of the inner sponge.  &  3.d6 \\

@@

\verb=  sponge_start_factor  = &   The sponge begins at sponge\_center\_density * sponge\_start\_factor.  &  3.333d0 \\
